### 2017-11-14 paper/sections/4_dynamic-policies.tex
paper: addresses #7
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Figure~\ref{src:dyn-cache} shows the algorithm we use to detect the key access
patterns in Figure~\ref{fig:keyspace-zoomed}. At each time step, we find the
lowest ID and compare against the local minimum, which is the smallest ID we
have seen thus far (Line 7). We also maintain the top and bottom of each fan
(Line 13) so we can tell the ``how much" policy the number of keys to evict
(Line 19).  If we move left to right, the local minimum never changes because
the local minimum will start small. If we move from right to left, the local
minimum changes at each access regime.  For points \(z\), \(y\), and \(x\), if
the local minimum is the same we are in a regime.  Processing \(y\), we set the
local minimum to be \(min(y, m_l)\), where \(m_l\) is the local minimum of the
previous time step of \(z\).  The algorithm incorrectly detects a regime change
if the local minimum of \(y\) is lower than local minimum of \(z\), since \(y\)
may have points {\it within} \(z\); recall that we are trying to detect the
whole fan, not just the bottom edge of each fan. We exchange runtime, in the
form of an O(n) algorithm, for simplicity. This approach avoids adding new
thresholds for new fan detection, such as space between key accesses, space
between key IDs, and window size of consecutive key accesses.

>>>>

Figure~\ref{src:dyn-cache} shows the algorithm we use to detect the key access
patterns. Iterating backwards through the keyspace trace, at each time step we
find the lowest key ID and compare against the lowest key ID we have seen so
far (Line 7). We also maintain the top and bottom of each fan (Line 13) so we
can tell the ``how much" policy the number of keys to evict (Line 19).  The
algorithm iterates backwards over the keyspace trace because a change in the
minimum value signals a new fan. No signal exists iterating left to right, as
the maximum value always increases and the minimum values at the bottom of each
fan are sparse.  For example, the maximum distance between values along the
bottom edge of the zoomed fan in Figure~\ref{fig:keyspace-zoomed} is 125
seconds, while the maximum distance between minimum values for the fan before
is 0 seconds. As a result of this sparseness, iterating left to right requires
a ``window size" parameter to determine when we think a minimum value will not
show up again.  We exchange runtime, in the form of an O(\(n\)) algorithm where
\(n\) is the number events, for simplicity because this approach avoids adding
new thresholds for fan detection ({\it e.g.}, space between key accesses, space
between key IDs, and window size of consecutive key accesses).

%For points \(z\), \(y\), and \(x\), if the
%local minimum is the same we are in a regime.  Processing \(y\), we set the
%local minimum to be \(min(y, m_l)\), where \(m_l\) is the local minimum of the
%previous time step of \(z\).  The algorithm incorrectly detects a regime change
%if the local minimum of \(y\) is lower than local minimum of \(z\), since \(y\)
%may have points {\it within} \(z\); recall that we are trying to detect the
%whole fan, not just the bottom edge of each fan.
